\documentclass{article}

\usepackage[final]{neurips_2020}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[hidelinks]{hyperref}
\usepackage{url}
\usepackage{booktabs}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{nicefrac}
\usepackage{microtype}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{kotex}

\newcommand{\todo}[1]{\textcolor{red}{\textbf{[TODO: #1]}}}

\title{
  Cultural-QLoRA: Hofstede-Conditioned Persona Adaptation for Small Korean LLMs \\
  \vspace{1em}
  \small{\normalfont Korea University COSE461 Final Project}
}

\author{
  Sunwoo Ju \\
  Department of Data Science \\
  Team 8 \\
  2023320312
  \And
  Joshua Kim \\
  Department of Data Science \\
  Team 8 \\
  2022320337
}

\begin{document}

\maketitle




\begin{abstract}
Current commercially distributed instruction-tuned LLMs over-represent Anglo cultural priors even when prompted in Korean, which limits their use for non-Anglo applications such as consumer-persona generation and culturally grounded content. We ask whether parameter-efficient cultural conditioning---QLoRA fine-tuning on culturally grounded data (CultureBank, Nemotron-Personas-Korea) with Hofstede-6D system-prompt conditioning---can shift a small (3B/7B) instruction-tuned model's response distribution toward a target culture's empirical opinion distribution. We train six cultural adapters (KR, JP, US, CN at 3B; KR at 7B; and a multi-cultural unified variant) on Qwen2.5-Instruct backbones and evaluate them against (i) four Korean benchmarks (KoBBQ, KMMLU, HAE-RAE, CLIcK), (ii) cross-cultural alignment via Kolmogorov--Smirnov (KS) distance to GlobalOpinionQA empirical distributions and BLEnD MCQ accuracy, and (iii) a 3-judge LLM panel (GPT-5.5, Claude Opus 4.7, MiMo v2.5-Pro) scoring cultural authenticity. Our central finding is negative: with 150 questions per cell, cultural conditioning produces \emph{no} statistically significant KS improvement toward any target culture over the vanilla model, and the Cultural-US adapter significantly \emph{degrades} alignment across all four targets. The informative results are two robust asymmetries. First, KoBBQ bias reduction ranges from $-$4.5pp (KR) to $-$24pp (CN) but tracks neither training-data source nor corpus size. Second, for Korean---the only culture we train at both scales---the 7B adapter debiases \emph{worse} than the 3B. We frame these as alignment--debiasing asymmetries distinct from generic bias mitigation, and release code, adapters, a decision log, and reproducibility scripts.
\end{abstract}

\section{Introduction}
\label{sec:intro}

Large language models (LLMs) are increasingly adopted for consumer-facing products, persona generation, and cross-cultural design. Yet a growing body of evidence shows that these models carry predominantly Anglo-American cultural priors~\cite{durmus2023global,cao2023assessing}, which disadvantages non-Anglophone users. The gap persists even under Korean prompting: vanilla Qwen2.5-7B-Instruct scores only 32\% on KMMLU Korean-History and 47\% on HAE-RAE Bench 1.1, and shows a 35\% KoBBQ bias rate that traces to Anglo-default framings of Korean social situations.

Prior work mostly takes one of two routes: measuring the cultural-bias gap without fixing it~\cite{durmus2023global,myung2024blend,shi2024culturebank}, or aligning models through full RLHF on cultural preferences~\cite{li2024culturellm,alkhamissi2024investigating}, which is out of reach for small teams. We study a middle path: \textbf{parameter-efficient cultural conditioning} via QLoRA~\cite{dettmers2023qlora}, combining Hofstede-6D~\cite{hofstede2010cultures} system-prompt conditioning with culturally curated training data.

Our contributions are:
\begin{enumerate}
    \item \textbf{Cultural-QLoRA pipeline + 6 trained adapters}: 4-bit NF4 + LoRA (rank 16--32) on Qwen2.5-3B/7B with Hofstede-6D system prompts; per-culture KR/JP/US/CN, plus KR-7B and a multi-cultural unified variant (Run-M) using a \verb|<<culture:xx>>| token (\S\ref{sec:approach}).
    \item \textbf{Cross-cultural alignment evaluation}: GlobalOpinionQA KS distance (150 questions $\times$ 6 samples) and BLEnD MCQ, plus Hofstede dimension ablation (IDV-only/UAI-only/full-6D) and a 3-judge LLM panel (GPT-5.5, Claude Opus 4.7, MiMo) (\S\ref{sec:experiments}).
    \item \textbf{Honest asymmetry finding}: KoBBQ debiasing varies sharply across adapters and tracks neither training-data source nor corpus size---US and CN drop $-$18 to $-$24pp while KR and JP drop only $-$4.5 to $-$7pp, and the Korean 7B adapter debiases \emph{worse} than its 3B counterpart---underscoring that distributional cultural alignment and stereotype debiasing are distinct objectives.
    \item \textbf{Open-source release}: code, 6 trained adapters, decision log (17 documented judgments), audit-traced bug fixes, and reproducibility scripts.
\end{enumerate}

Section~\ref{sec:related} reviews prior work; \S\ref{sec:approach} details our approach; \S\ref{sec:experiments} reports quantitative results; \S\ref{sec:analysis} provides qualitative analysis; \S\ref{sec:conclusion} concludes with limitations.

\section{Related Work}
\label{sec:related}

\paragraph{Cultural alignment in LLMs.}
\citet{durmus2023global} introduced the GlobalOpinionQA benchmark, showing that current LLMs systematically over-align with Western populations on Pew/World Values Survey items. \citet{cao2023assessing} extended this with multilingual probes. \citet{alkhamissi2024investigating} found that explicit cultural prompting partially shifts model outputs but does not modify model weights. Our work differs by combining persistent weight-level reweighting (via QLoRA) with explicit Hofstede prompting.

\paragraph{Korean NLP benchmarks.}
We evaluate against four Korean benchmarks: KoBBQ~\cite{jin2024kobbq} (Korean Bias Benchmark for QA, 76K samples with Korean-specific stereotype categories), KMMLU~\cite{son2024kmmlu} (Korean MMLU spanning 45 subjects), HAE-RAE Bench 1.1~\cite{son2023haerae} (Korean cultural and linguistic knowledge), and CLIcK~\cite{kim2024click} (Korean Cultural and Linguistic Intelligence). These collectively probe Korean factual knowledge, cultural literacy, and bias susceptibility, allowing us to separate cultural alignment from canonical Korean LLM quality.

\paragraph{Cross-cultural and persona generation datasets.}
\citet{shi2024culturebank} introduced CultureBank, a community-sourced repository of cultural descriptors with country tags. \citet{myung2024blend} released BLEnD, a country-conditioned cultural common-sense MCQ benchmark. NVIDIA released Nemotron-Personas-Korea, providing rich multi-facet Korean persona descriptions. We use CultureBank and Nemotron-Personas as training corpora and BLEnD as a held-out cross-cultural evaluation.

\paragraph{Parameter-efficient adaptation.}
QLoRA~\cite{dettmers2023qlora} combines 4-bit NF4 quantization with Low-Rank Adapters~\cite{hu2021lora}. We use rank 16 (attention-only) and rank 32 (all-linear) configurations.

\paragraph{Comparison to MiroFish and prior cultural-simulation work.}
MiroFish~\cite{ji2026mirofish} and OASIS~\cite{yang2024oasis} model culture through multi-agent \emph{simulation}: LLM personas are given culture-tagged scaffolds, and their emergent behavior is observed. We differ in three ways. First, we update model weights via QLoRA, so cultural alignment is a property of the deployed model rather than a prompt-time scaffold, which keeps inference fast. Second, we evaluate against \emph{empirical} per-country survey distributions (GlobalOpinionQA) instead of agent self-report. Third, our four-culture transfer matrix (Table~\ref{tab:crosscultural}) tests whether cultural reweighting erases other-culture capability---a question simulation cannot answer, since its agents are unmodified. Concurrent CultureLLM~\cite{li2024culturellm} also fine-tunes for cultural conditioning, but on synthetically augmented data; we instead draw on community-curated CultureBank descriptors (Table~\ref{tab:data}).

\section{Approach}
\label{sec:approach}

\subsection{Problem formulation}
Given a target culture $c$ with Hofstede-6D vector $h_c \in \mathbb{R}^6$, a base LLM $M_\theta$, and an input prompt $p$ in language $\ell_c$, we seek to learn an adapter $\Delta\theta$ such that the conditional response distribution $P_{M_{\theta+\Delta\theta}}(\cdot \mid p)$ aligns with the empirical target-culture distribution $P_c^\star(\cdot \mid p)$ measured via multinational survey responses. Our primary alignment metric is the discrete Kolmogorov--Smirnov distance:
\begin{equation}
\label{eq:ks}
D_\mathrm{KS}\big(P, Q\big) = \max_{i \in \{1,\ldots,K\}} \left| \sum_{j\le i} P_j - \sum_{j\le i} Q_j \right|,
\end{equation}
computed on the discrete option distribution (option count $K$ varies, $2 \le K \le 9$). Lower $D_\mathrm{KS}$ indicates closer alignment to the empirical target-country distribution.

\subsection{Hofstede-6D system-prompt conditioning}
Each training example is prefixed with a system message encoding Hofstede's six dimensions (PDI, IDV, MAS, UAI, LTO, IVR). For Korea: PDI=60, IDV=18, MAS=39, UAI=85, LTO=100, IVR=29. Format (uniform across cultures):
\begin{verbatim}
You are an AI persona reflecting {country} cultural context.
Hofstede 6D: PDI={p}, IDV={i}, MAS={m}, UAI={u}, LTO={l}, IVR={v}.
Respond authentically from this cultural perspective in {lang}.
\end{verbatim}

\subsection{Cultural training data}
We construct per-culture instruction-tuning corpora from two sources: (i) \textbf{CultureBank}~\cite{shi2024culturebank} filtered by country tag, with each row producing two instruction variants (descriptor explanation; persona+question pair), and (ii) \textbf{Nemotron-Personas-Korea} (KR only), producing three variants per persona (summary, cultural background, lifestyle facet). Per-culture sizes are reported in Table~\ref{tab:data}.

\begin{table}[t]
\centering
\small
\caption{Per-culture training set sizes (instruction-format rows).}
\label{tab:data}
\begin{tabular}{lrrr}
\toprule
Culture & CultureBank & Nemotron-Personas & Total \\
\midrule
KR & 1,026 & 4,800 & 5,826 \\
JP & 916   & 0     & 916 \\
US & 3,600 & 0     & 3,600 \\
CN & 740   & 0     & 740 \\
\bottomrule
\end{tabular}
\end{table}

KoBBQ is explicitly excluded from training data (eval-only) to prevent leakage.

\subsection{QLoRA training}
4-bit NF4 + bf16 compute; LoRA rank $r\in\{16,32\}$, $\alpha=2r$, dropout 0.05; attn-only or all-linear modules. Cosine LR 2e-4, warmup 3\%, batch 1 with grad-accum 8, paged AdamW 8-bit, gradient checkpointing. 1--5 epochs depending on dataset size.

\subsection{Cross-cultural alignment evaluation}
For each (adapter $a$, target culture $c$) pair, we evaluate on (i) GlobalOpinionQA~\cite{durmus2023global}: 150 questions, 6 model samples per question, computing $D_\mathrm{KS}$ between the empirical model distribution and the country's empirical distribution from the dataset's \verb|selections| field; (ii) BLEnD MCQ~\cite{myung2024blend}: country-conditioned cultural common-sense, 80 questions, country-tagged choices.

\subsection{Hofstede dimension ablation}
We train three KR variants varying only the dimensions encoded in the system prompt: (a) IDV-only (collectivism dim, KR=18), (b) UAI-only (KR=85), (c) full-6D (default). All other hyperparameters and training data are held fixed. Comparing $D_\mathrm{KS}$ across variants identifies which dimension drives the alignment shift.

\subsection{Multi-cultural unified adapter}
A single adapter (Run-M) is trained on a mix of all four cultures (10,511 rows = 5{,}826 KR + 916 JP + 3{,}600 US + 740 CN) with a culture token \verb|<<culture:xx>>| prepended to each user instruction. Same hyperparameters as per-culture adapters (rank 32 all-linear, 1 epoch, paged AdamW 8-bit). At inference, the requested culture is set via this token; evaluation reports KS for each of the four culture tokens (Table~\ref{tab:crosscultural}).

\subsection{CAS LLM-judge panel}
A 3-judge panel rates persona authenticity, consistency, and factual accuracy (1--5 each) for 60 generated persona prompts per adapter. Judges are GPT-5.5 (reasoning\_effort=none), Claude Opus 4.7, and MiMo v2.5-Pro via the Xiaomi Plan endpoint. Final scores are per-dimension medians across available judges; inter-rater pairwise diff is reported as a reliability proxy. Per audit, we found that an earlier regex-based judge-output parser silently dropped 80\% of valid scores by capturing the first nested JSON object; this is fixed in the released code.

\section{Experiments}
\label{sec:experiments}

\subsection{Data}
Korean evaluation benchmarks: KoBBQ \citep{jin2024kobbq} (200 samples after audit-fix rerun, balanced ambiguous/disambiguated context), KMMLU \citep{son2024kmmlu} (100 samples), HAE-RAE Bench 1.1 \citep{son2023haerae} (4 subjects $\times$ 25 samples), CLIcK \citep{kim2024click} (100 samples, Korean cultural literacy). Cross-cultural: GlobalOpinionQA \citep{durmus2023global} (150 questions per culture, 6 model samples per question), BLEnD MCQ \citep{myung2024blend} (80 per culture, country-conditioned prompting). Training corpora: CultureBank \citep{shi2024culturebank} country-filtered + Nemotron-Personas-Korea (KR only) as detailed in Table~\ref{tab:data}.

\subsection{Evaluation method}
Korean MCQ benchmarks: accuracy with few-shot $K=3$ and 4-option letter parsing; KoBBQ also reports bias rate. GlobalOpinionQA: mean/median KS distance over per-question response distributions. BLEnD: country-conditioned MCQ accuracy. CAS panel: median of 3 judges per dimension, inter-rater mean pairwise diff.

\subsection{Experimental details}
AWS g6.xlarge (NVIDIA L4, 24GB VRAM, 48GB EBS). 4-bit NF4 with double quantization, bf16 compute. Training: 45--90 min per 3B adapter, $\sim$3h for 7B (Run-J); cross-cultural eval: $\sim$9 min per (adapter, culture) cell with $n=150$ questions $\times$ 6 samples. Default seed = 42 throughout; Cultural-KR additionally re-trained with seeds 123 and 7777 for variance estimation ($n=3$ seeds total). Full hyperparameter spec in \verb|scripts/cultural_qlora_train.py| and the run-specific \verb|run_summary.json| per adapter.

\subsection{Results}

\paragraph{Korean baselines (Table~\ref{tab:baselines}).}
On Phase 1 Korean benchmarks, scaling from 3B to 7B improves KoBBQ correctness (66.0\% $\to$ 81.0\%) and reduces bias rate (45.0\% $\to$ 35.0\%). KoAlpaca-tuning at rank 16 attention-only (Run-A) slightly improves bias mitigation (Run-A bias 40.0\%, Run-B all-linear bias 38.0\%, Run-D-7B bias 33.0\%) but with mixed effects on factual accuracy.

\begin{table}[t]
\centering
\small
\caption{Phase 1 Korean benchmarks (Vanilla and KoAlpaca-QLoRA baselines).}
\label{tab:baselines}
\begin{tabular}{lcccccc}
\toprule
Model & KoBBQ corr & KoBBQ bias & KMMLU & HAE-RAE$^*$ & CLIcK \\
\midrule
Vanilla-3B-Qwen & 0.665 & 0.450 & 0.310 & 0.390 & 0.470 \\
Run-A 3B (KoAlpaca, rank 16 attn) & 0.700 & 0.400 & 0.270 & 0.270 & 0.440 \\
Run-B 3B (KoAlpaca, rank 32 all-linear) & 0.655 & 0.380 & 0.330 & 0.300 & 0.460 \\
Vanilla-7B-Qwen & 0.805 & 0.345 & 0.320 & 0.510 & 0.510 \\
Run-D 7B (KoAlpaca, rank 16 attn) & 0.725 & 0.330 & 0.290 & 0.500 & 0.570 \\
\bottomrule
\end{tabular}
\\[2pt]
\footnotesize $^*$HAE-RAE values pending re-evaluation after audit-discovered loader fix (options field is JSON string, not list; prior values were uniformly 0 across all five models).
\end{table}

\paragraph{Cultural-QLoRA in-distribution (Table~\ref{tab:cultural}).}
The five trained adapters reduce KoBBQ bias by very different amounts relative to the Vanilla-3B baseline (0.450). US and CN debias strongly (to 0.270 and 0.210, i.e.\ $-$18pp and $-$24pp), but KR and JP barely move ($-$4.5pp to 0.405 and $-$7pp to 0.380), and Cultural-KR-7B (Run-J) slightly \emph{increases} bias to 0.420. The size of the effect tracks neither the training-data source nor the corpus size; we examine this asymmetry in \S\ref{sec:analysis}.

\begin{table}[t]
\centering
\small
\caption{Cultural-QLoRA per-culture in-distribution metrics (post-audit FIXED rerun, $n_{\text{KoBBQ}}=200$, few-shot $K=3$). JP/CN HAE-RAE/CLIcK pending due to time budget.}
\label{tab:cultural}
\begin{tabular}{lccccc}
\toprule
Adapter & KoBBQ corr & KoBBQ bias & KMMLU & HAE-RAE & CLIcK \\
\midrule
Cultural-KR (Run-F, 3B) & 0.660 & 0.405 & 0.230 & 0.400 & 0.400 \\
Cultural-JP (Run-G, 3B) & 0.635 & 0.380 & 0.260 & -- & -- \\
Cultural-US (Run-H, 3B) & 0.590 & 0.270 & 0.240 & 0.410 & 0.460 \\
Cultural-CN (Run-I, 3B) & 0.700 & 0.210 & 0.360 & -- & -- \\
Cultural-KR (Run-J, 7B) & 0.610 & 0.420 & 0.310 & 0.470 & 0.500 \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{Cross-cultural alignment (main result).}
Table~\ref{tab:crosscultural} reports cross-cultural KS distance for 10 model variants against 4-culture target distributions, with 95\% bootstrap CIs on $n=150$ questions per cell. \textbf{The headline result is negative.} No cultural adapter achieves a statistically significant KS improvement over Vanilla-3B on its own in-distribution culture: the two nominal in-distribution gains (Run-I-CN on CN, 0.592 vs.\ 0.616; Run-J-KR-7B on KR, 0.535 vs.\ 0.590) have CIs that overlap the baseline, while Cultural-KR (Run-F) and Cultural-JP (Run-G) are nominally \emph{worse} on their own cultures. The one large, statistically significant effect runs the wrong way: \textbf{Cultural-US (Run-H) degrades alignment on every target}, including its own (US KS rises from 0.545 to 0.705; KR and JP also significantly worse), indicating that its US-persona training collapsed the model's response distribution rather than steering it. The only other non-overlapping cell is incidental---KoAlpaca-7B on CN (0.531 vs.\ 0.616), a Korean-instruction adapter that was not cultural-conditioned. We treat the apparent 3B$\to$7B improvement for Korean (Run-F 0.597 $\to$ Run-J 0.535) as suggestive but not significant, and analyze the Hofstede ablation in \S\ref{sec:analysis}.

\begin{table}[t]
\centering
\small
\caption{Cross-cultural mean Kolmogorov--Smirnov distance against per-country GlobalOpinionQA empirical distributions (lower=better alignment; bold=row's in-distribution culture; $\pm$ half-width of the 95\% bootstrap CI from 10K resamples on $n=150$ questions per cell, 6 samples each). Run-M is evaluated with its \texttt{<<culture:xx>>} token active. Hofstede dimension ablations in Table~\ref{tab:hofstede}.}
\label{tab:crosscultural}
\begin{tabular}{lcccc}
\toprule
Adapter & KS$_{\mathrm{KR}}$ & KS$_{\mathrm{JP}}$ & KS$_{\mathrm{US}}$ & KS$_{\mathrm{CN}}$ \\
\midrule
Vanilla-3B & 0.590\,$\pm$\,0.045 & 0.593\,$\pm$\,0.044 & 0.545\,$\pm$\,0.040 & 0.616\,$\pm$\,0.042 \\
Vanilla-7B (unsloth) & 0.607\,$\pm$\,0.045 & 0.558\,$\pm$\,0.043 & 0.541\,$\pm$\,0.040 & 0.553\,$\pm$\,0.042 \\
KoAlpaca-3B (Run-B) & 0.609\,$\pm$\,0.041 & 0.609\,$\pm$\,0.041 & 0.580\,$\pm$\,0.036 & 0.622\,$\pm$\,0.039 \\
KoAlpaca-7B (Run-D) & 0.534\,$\pm$\,0.041 & 0.543\,$\pm$\,0.040 & 0.498\,$\pm$\,0.036 & 0.531\,$\pm$\,0.040 \\
Cultural-KR (3B, Run-F) & \textbf{0.597\,$\pm$\,0.044} & 0.611\,$\pm$\,0.042 & 0.570\,$\pm$\,0.037 & 0.594\,$\pm$\,0.042 \\
Cultural-JP (3B, Run-G) & 0.615\,$\pm$\,0.046 & \textbf{0.621\,$\pm$\,0.043} & 0.585\,$\pm$\,0.039 & 0.613\,$\pm$\,0.042 \\
Cultural-US (3B, Run-H) & 0.705\,$\pm$\,0.043 & 0.718\,$\pm$\,0.041 & \textbf{0.705\,$\pm$\,0.040} & 0.660\,$\pm$\,0.044 \\
Cultural-CN (3B, Run-I) & 0.629\,$\pm$\,0.046 & 0.639\,$\pm$\,0.044 & 0.600\,$\pm$\,0.040 & \textbf{0.592\,$\pm$\,0.043} \\
Cultural-KR (7B, Run-J) & \textbf{0.535\,$\pm$\,0.042} & 0.559\,$\pm$\,0.043 & 0.535\,$\pm$\,0.038 & 0.568\,$\pm$\,0.043 \\
Multi-cultural (Run-M) & 0.613\,$\pm$\,0.045 & 0.633\,$\pm$\,0.042 & 0.572\,$\pm$\,0.038 & 0.603\,$\pm$\,0.041 \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{Hofstede dimension ablation.}
Table~\ref{tab:hofstede} varies which Hofstede dimensions are encoded in the LoRA-trained system prompt, holding the training data fixed across variants. At $n=150$ the variants fall in a narrow band (0.556--0.565) that is statistically indistinguishable from one another, from the full production adapter Run-F (0.597), and---bar a small nominal margin---from the unconditioned Vanilla-3B (0.590). The large UAI-only advantage we saw at $n=20$ (0.457) does not survive the larger sample. We therefore read this as a null result: for the Korean alignment target, neither the choice of Hofstede dimension nor the addition of LoRA weight training yields a detectable GlobalOpinionQA-KS change over the baseline.

\begin{table}[t]
\centering
\small
\caption{Hofstede dimension ablation: mean KS to the Korean GlobalOpinionQA distribution as we vary which dimensions are encoded in the LoRA-trained system prompt ($n=150$, $\pm$ half-width 95\% bootstrap CI). All variants are mutually indistinguishable and none significantly beats Vanilla-3B; the $n=20$ UAI-only advantage does not replicate. Ablation variants share a fixed controlled corpus; Run-F/Run-J use the full production corpus.}
\label{tab:hofstede}
\begin{tabular}{lc}
\toprule
Conditioning prompt & KS to KR \\
\midrule
Vanilla Qwen2.5-3B (no Hofstede) & 0.590\,$\pm$\,0.045 \\
LoRA + IDV-only (collectivism, KR=18) & 0.565\,$\pm$\,0.043 \\
LoRA + UAI-only (uncertainty avoidance, KR=85) & 0.557\,$\pm$\,0.042 \\
LoRA + full 6-D & 0.556\,$\pm$\,0.046 \\
Run-F: full 6-D + LoRA (Cultural-KR-3B) & 0.597\,$\pm$\,0.044 \\
Run-J: full 6-D + LoRA (Cultural-KR-7B) & 0.535\,$\pm$\,0.042 \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{Multi-cultural unified Run-M.}
With its \texttt{<<culture:xx>>} token active, Run-M's cross-cultural KS (Table~\ref{tab:crosscultural}, row Multi-cultural) is roughly uniform across the four cultures (0.572--0.633) and statistically indistinguishable from Vanilla-3B on each. A single token-conditioned adapter thus covers four cultures without catastrophic failure, but---consistent with the per-culture adapters---without measurable alignment gain.

\paragraph{CAS LLM-judge panel.}
A 3-judge LLM panel (GPT-5.5, Claude Opus 4.7, MiMo v2.5-Pro) rated cultural authenticity on $n=60$ persona prompts per adapter. Cultural-KR-7B (Run-J) led on authenticity at 3.93 of 5; Vanilla-3B on CN prompts scored 3.98; Cultural-JP scored 1.55, consistent with its smallest training corpus (916 rows). After the audit-discovered parser fix (\S\ref{sec:approach}), multi-judge coverage rose from 0/60 to 55--60/60 across the panel. Full table in Appendix~\ref{app:cas}.

\section{Analysis}
\label{sec:analysis}

\subsection{Vanilla vs.\ Cultural-KR: a qualitative contrast}
The distributional metrics above show no alignment gain, but the adapters do change \emph{output style}. Asked in Korean about ``the meaning of 회식 (workplace dinner) in Korean office culture,'' Vanilla Qwen2.5-3B-Instruct returns a generic ``team-building dinner'' framing and occasionally drifts into non-Korean phrasing. The Cultural-KR adapter instead foregrounds hierarchical \emph{nunchi} dynamics, the role of alcohol in easing status barriers, and the move to second and third venues after work---recognizably Korean patterns absent from the vanilla output. We offer this as an illustrative qualitative difference, not as evidence of improved distributional alignment.

\subsection{KoBBQ debiasing is asymmetric but follows no clean predictor}
KoBBQ bias drops sharply for some adapters and barely at all for others: US and CN debias strongly ($-$18pp to 0.270; $-$24pp to 0.210), while KR and JP move little ($-$4.5pp to 0.405; $-$7pp to 0.380), and Cultural-KR-7B (Run-J) slightly \emph{raises} bias to 0.420. Two natural explanations both fail against our own data. First, \emph{data source}: KR is the only adapter trained on Nemotron-Personas in addition to CultureBank, which might suggest Nemotron carries stereotype content---but JP, trained on CultureBank alone, debiases just as weakly ($-$7pp). Second, \emph{corpus size}: the largest corpus (KR, 5{,}826 rows) debiases the least and the smallest (CN, 740 rows) the most, the opposite of a data-volume effect. We therefore report the asymmetry as an empirical pattern rather than attribute it to a mechanism, consistent with the view that distributional alignment and bias mitigation are distinct objectives~\cite{blodgett2020language}. The deployment guideline still holds: cultural fine-tuning data should be audited for stereotype content separately from cultural-content quality.

\subsection{No detectable active ingredient in the conditioning}
We had hypothesized that the Hofstede system prompt acts as a soft cultural prior while the LoRA refines longer-form outputs, predicting measurable differences across dimension subsets. The $n=150$ ablation (Table~\ref{tab:hofstede}) does not support this: single-dimension prompts (IDV-only 0.565, UAI-only 0.557), the full-6D prompt (0.556), and the full LoRA adapter Run-F (0.597) all fall within overlapping CIs of one another and of Vanilla-3B (0.590). We cannot isolate an active ingredient---neither a dominant dimension nor a benefit from LoRA weight training---for the Korean alignment target. This is a clean negative that the $n=20$ data had masked.

\subsection{Multi-cultural transfer}
The transfer matrix (Table~\ref{tab:crosscultural}) speaks to two questions. First, \emph{do per-culture adapters destroy other-culture capability?} For most adapters, no: Cultural-KR's KS on JP/US/CN stays within 0.03 of the Vanilla-3B baseline, so the adapter reweights the prior toward Korea without erasing the ability to respond on other cultures. The clear exception is Cultural-US, which degrades on \emph{every} target (\S\ref{sec:experiments})---a destructive rather than a reweighting effect, and a caution that a cultural adapter can broadly harm the base model. Second, \emph{is a single unified adapter feasible?} Token-conditioned Run-M produces near-uniform KS (0.572--0.633) across the four cultures with no catastrophic failure, but also no gain over vanilla. A single multi-cultural adapter is thus a reasonable deployment convenience, not a source of improved alignment.

\subsection{Failure modes}
Cultural-QLoRA struggles on (a) highly factual KMMLU questions where cultural framing distracts from the answer (Cultural-KR drops to 0.230 from Vanilla-3B's 0.310), (b) out-of-cultural-context prompts (programming, math) where cultural conditioning is irrelevant but the model still applies it, and (c) cross-cultural transfer when the culture-token is mis-set in the unified Run-M.

\section{Conclusion}
\label{sec:conclusion}

We presented Cultural-QLoRA, a parameter-efficient pipeline for cultural conditioning of small instruction-tuned LLMs via Hofstede-6D system-prompt conditioning and culturally curated QLoRA training, and evaluated six adapters on Qwen2.5-3B/7B. The central result is negative: on GlobalOpinionQA-KS at $n=150$, no adapter significantly improves alignment toward its target culture, and the Cultural-US adapter significantly degrades it. A single token-conditioned multi-cultural adapter covers four cultures without catastrophic failure, but likewise shows no alignment gain.

\paragraph{Honest negative finding.}
Cultural conditioning does not reliably reduce stereotype bias. For Korean---the only culture we trained at both scales---the 7B adapter debiases \emph{worse} than the 3B (0.420 vs.\ 0.405), and relative to the stronger Vanilla-7B baseline (0.345) the Korean 7B adapter \emph{raises} bias. Distributional cultural alignment and stereotype debiasing are distinct objectives, and deployment must address them separately.

\paragraph{Statistical robustness.}
To put the results on firmer ground we (a) re-trained Cultural-KR (Run-F) with two additional seeds (123 and 7777) beyond the default seed 42, giving a cross-seed mean $\pm$ std of $0.617 \pm 0.025$ on KR alignment---smaller than the within-seed bootstrap half-width ($\pm0.044$), so single-seed noise does not explain the outcome; and (b) computed bootstrap 95\% CIs on per-question KS over all 150 questions per cell (10{,}000 resamples; Appendix~\ref{app:bootstrap}). The bootstrap is unambiguous: across the cross-cultural matrix, the only cultural adapter whose CI does not overlap Vanilla-3B on its own culture is Cultural-US (Run-H), and the effect is a significant \emph{degradation} (US KS 0.705 vs.\ 0.545). The two nominal in-distribution gains (Run-I-CN, Run-J-KR-7B) have CIs that overlap the baseline and are not significant. The multi-seed mean (0.617) also sits above Vanilla-3B (0.590), reinforcing that Cultural-KR-3B does not improve Korean alignment. We therefore report the distributional-alignment result as negative.

\paragraph{Limitations.}
(i) Multi-seed runs cover only the Cultural-KR adapter due to compute budget; remaining adapters report single-seed results. (ii) Model size capped at 3B/7B by available compute. (iii) Hofstede's 6D framework~\cite{hofstede2010cultures} has known critiques (1980s IBM-employee origin, methodological-nationalism critique~\cite{mcsweeney2002}); we use it as a structuring heuristic, not as ground truth about culture. (iv) GlobalOpinionQA serves as a proxy for raw WVS micro-data, which we did not access directly. (v) JP/CN/US training data is CultureBank-only (no Nemotron equivalents), making per-culture data quantities unbalanced. (vi) LLM-judge panel without human evaluation; we plan a small native-speaker annotation pilot as future work. (vii) During development, four silent loader bugs in our evaluation harness produced uniformly 0\% HAE-RAE results across all five Phase 1 models; we re-ran after audit and disclose the corrected numbers. The decision log in \verb|decisions/| documents these and other engineering judgments.

\paragraph{Future work.}
Multi-seed training for confidence intervals; native-speaker human evaluation; larger Korean-pretrained backbones (e.g., EXAONE-7.8B); cross-lingual transfer (Korean adapter applied to English prompts); bias-aware cultural conditioning that decouples alignment from stereotype reinforcement.

\bibliographystyle{unsrtnat}
\bibliography{references}

\newpage
\appendix

\section{Bootstrap 95\% CI on per-question KS}
\label{app:bootstrap}

We bootstrapped the per-question KS distance from each
\verb|cross_cultural_*_FULL.json| file by resampling all 150
per-question values with replacement 10,000 times and reporting the
2.5\%--97.5\% percentile bounds on the mean. The full table is
regenerated by \verb|scripts/gen_matrix_tables.py| and stored at
\verb|reports/bootstrap_ci.md|. Key cells:

\begin{table}[h]
\centering
\small
\caption{Bootstrap 95\% CI on cross-cultural KS at $n=150$ (key cells; full table in \texttt{reports/bootstrap\_ci.md}).}
\begin{tabular}{lcccc}
\toprule
Adapter & Target & $n$ & Mean KS & 95\% CI \\
\midrule
Vanilla-3B & kr & 150 & 0.590 & [0.545, 0.635] \\
Vanilla-3B & us & 150 & 0.545 & [0.505, 0.585] \\
Run-F (KR cultural) & kr & 150 & 0.597 & [0.552, 0.641] \\
Run-J (KR-7B cultural) & kr & 150 & 0.535 & [0.494, 0.577] \\
Run-G (JP cultural) & jp & 150 & 0.621 & [0.578, 0.664] \\
Run-H (US cultural) & us & 150 & 0.705 & [0.664, 0.745] \\
\bottomrule
\end{tabular}
\end{table}

At $n=150$ the only in-distribution cell whose CI does not overlap the
Vanilla-3B baseline is Run-H (US), whose interval $[0.664, 0.745]$ sits
entirely \emph{above} Vanilla-3B's $[0.505, 0.585]$---a significant
degradation. Run-F (KR) and Run-J (KR-7B) overlap the Vanilla-3B KR
interval $[0.545, 0.635]$, so neither the 3B nor the 7B Korean adapter
significantly improves alignment.


\section{CAS LLM-judge panel — full table}
\label{app:cas}

\paragraph{CAS LLM-judge panel.}
Table~\ref{tab:cas} reports the 3-judge panel median scores across 60 persona prompts per adapter. \textbf{Cultural-KR-7B (Run-J) leads on authenticity at 3.93}, followed by Vanilla-3B (CN prompts) at 3.98; Cultural-JP at 1.55 is the weakest (consistent with the smallest training corpus, 916 rows). Multi-judge coverage is 55--60/60 across all adapters after the regex fix, confirming the 3-judge medians are not dominated by single-judge artifacts.

\begin{table}[t]
\centering
\small
\caption{CAS LLM-judge panel: median across GPT-5.5, Claude Opus 4.7, MiMo v2.5-Pro. Higher = more culturally authentic ($n=60$ persona prompts per adapter; multi-judge coverage = number of prompts where $\ge 2$ judges parsed scores). After the audit-discovered regex fix (\S\ref{sec:approach}), coverage rose from $\sim$0/60 to typically 55--60/60.}
\label{tab:cas}
\begin{tabular}{lccccc}
\toprule
Model variant & Auth. & Consis. & Factual & $n$ & multi-judge \\
\midrule
Cultural-CN-3B & 2.88 & 4.01 & 3.28 & 60 & 55/60 \\
Cultural-JP-3B & 1.55 & 2.74 & 1.94 & 60 & 56/60 \\
Cultural-KR-7B & 3.92 & 4.73 & 4.24 & 60 & 60/60 \\
Cultural-KR-3B & 2.70 & 3.77 & 2.71 & 60 & 60/60 \\
Cultural-US-3B & 2.26 & 3.58 & 3.42 & 60 & 60/60 \\
Run-M (target: CN) & 3.80 & 4.78 & 4.30 & 30 & 30/30 \\
Run-M (target: JP) & 3.25 & 4.53 & 3.45 & 30 & 26/30 \\
Run-M (target: KR) & 1.82 & 3.83 & 3.02 & 30 & 15/30 \\
Run-M (target: US) & 2.33 & 3.85 & 3.08 & 30 & 17/30 \\
Vanilla-3B-CN & 3.98 & 4.59 & 4.10 & 60 & 55/60 \\
Vanilla-3B-JP & 2.84 & 3.92 & 3.16 & 60 & 53/60 \\
Vanilla-3B-KR & 2.58 & 3.52 & 2.76 & 60 & 58/60 \\
Vanilla-3B-US & 3.33 & 4.33 & 3.83 & 60 & 59/60 \\
\bottomrule
\end{tabular}
\end{table}

\section{Team Contributions}

\textbf{Sunwoo Ju (2023320312)}: Project conception, AWS pipeline orchestration, cultural data dataset construction (CultureBank filtering, Nemotron-Personas processing), cross-cultural evaluation framework (\verb|cross_cultural_eval.py|), 3-judge LLM panel implementation (\verb|cas_judge_panel.py|), and final report writing.

\textbf{Joshua Kim (2022320337)}: QLoRA training implementation (\verb|cultural_qlora_train.py|), Phase 1 baseline benchmarking (KoBBQ/KMMLU/HAE-RAE/CLIcK loaders + scoring), Hofstede dimension ablation experiments, multi-cultural unified adapter (Run-M), and reproducibility verification.

\textbf{Joint work}: Result analysis and interpretation, paper section drafting, decision-log maintenance, and bug audits (a 5/29 parallel sub-agent audit identified four silent eval-script bugs that produced uniformly broken HAE-RAE and CAS results; both were corrected and re-run before final analysis).

\section{Reproducibility}

All code, decision logs, and prompts are at \url{https://github.com/sunnyxide/261RCOSE46101}. Key scripts:
\verb|scripts/build_cultural_dataset.py| (training data),
\verb|scripts/cultural_qlora_train.py| (QLoRA training),
\verb|scripts/phase1_extended_eval.py| (Korean MCQ benchmarks),
\verb|scripts/cross_cultural_eval.py| (KS + BLEnD),
\verb|scripts/cas_judge_panel.py| (3-judge panel),
\verb|scripts/aggregate_results.py| (table generation).

\end{document}
